---
title: "Introduction to linreg"
output: rmarkdown::html_vignette
description: >
  This file will explain how the linreg package works and how to use it on a well known dataset.
vignette: >
  %\VignetteIndexEntry{Introduction to linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab4LinearRegression)
```

# Description of Function  
This function takes a given formula with independent and dependent variables as well as a dataset and creates a linear regression model. The function returns an object of an RC class. Different methods are implemented for this object in the RC objected oriented system and are detailed below.  

## Methods availble in this function  
* 'print()' prints out the coefficients and coefficient names for given dataset.
* 'plot()' creates two plots based off of data, residuals vs fitted values and scale to location values.
* 'resid()' returns the vector of residuals.
* 'pred()' returns the predicted values.
* 'coef()' returns the coefficients as a named vector.
* 'summary()' returns the coefficients with their standard error, t-value and p-value as well as the estimate of residual standard error and the degrees of freedom in the model.

### How to use function:  
1. load data
    *example: load(iris)  
1. set object to function, including the formula wanting to be used and the data 
    *example: lin <- linreg(Petal.Length~Species, iris)  
1. implement chosen method by subsetting 
    *examples: 
        *lin$print() 
        *lin$plot()
        *lin$summary()
